Pre- and Post-Debate Democratic Primary Data: Twitter, Google Trends, and Polls

### 2019-12-08 Presentation/SURV727_FinalPresentation_Padgett_Thiam.Rmd
Update SURV727_FinalPresentation_Padgett_Thiam.Rmd

## Pre-debate number of tweets 
```{r, fig.cap="Pre-debate Mentions in Tweets, by Candidate"}
props_tab1 %>%
  filter(Cat == "TRUE") %>%
  ggplot() +
  geom_col(mapping = aes(x = reorder(Candidate, -Count), y=Count, fill = Candidate)) +
    labs(x = "Democatric Party Canditates", 
       y = "Number of Tweets", 
       caption = "Source: Twiiter") 
```

## Post-debate number of tweets 
```{r, fig.cap="Post-debate Mentions in Tweets, by Candidate"}
props_tab2 %>%
  filter(Cat == "TRUE") %>%
  ggplot() +
  geom_col(mapping = aes(x = reorder(Variable, -Count), y=Count, fill = Variable)) +
    labs(x = "Democatric Party Canditates", 
       y = "Number of Tweets", 
       caption = "Source: Twiiter")

>>>>

## Pre-debate number of tweets 
```{r, fig.cap="Pre-debate Mentions in Tweets, by Candidate"}
props_tab1 %>%
  filter(Cat == "TRUE") %>%
  ggplot() +
  geom_col(mapping = aes(x = reorder(Candidate, -Count), y=Count, fill = Candidate)) +
    labs(x = "Democatric Party Canditates", 
       y = "Number of Tweets", 
       caption = "Source: Twitter") 
```

## Post-debate number of tweets 
```{r, fig.cap="Post-debate Mentions in Tweets, by Candidate"}
props_tab2 %>%
  filter(Cat == "TRUE") %>%
  ggplot() +
  geom_col(mapping = aes(x = reorder(Candidate, -Count), y=Count, fill = Candidate)) +
    labs(x = "Democatric Party Canditates", 
       y = "Number of Tweets", 
       title = "Post Debate candidates mentions in Tweets", 
       caption = "Source: Twitter")

## Tweets location pre-debate 
```{r, fig.cap="Pre-debate Mentions in Tweets, by Candidate & location"}

  ggplot() +
  geom_col(mapping = aes(x = reorder(Candidate, -Count), y=Count, fill = Candidate)) +
    labs(x = "Democatric Party Canditates", 
       y = "Number of Tweets", 
       title = "Post Debate candidates mentions in Tweets", 
       caption = "Source: Twitter")

## Tweets location post-debate 
```{r, fig.cap="Post-debate Mentions in Tweets, by Candidate & location"}

  ggplot() +
  geom_col(mapping = aes(x = reorder(Candidate, -Count), y=Count, fill = Candidate)) +
    labs(x = "Democatric Party Canditates", 
       y = "Number of Tweets", 
       title = "Post Debate candidates mentions in Tweets", 
       caption = "Source: Twitter")
